---
title: "PH 142 Quiz 8 Spring 2021"
author: "Your name here"
output: word_document
---

## Instructions
Return via email as a Word document to ph142@berkeley.edu. Do not handwrite your answers or convert to a PDF. Please highlight your answer(s) for any multiple choice questions and type your answer where indicated for short answer or fill in the blank questions.

```{r, include = F}
knitr::opts_chunk$set(include = F, echo = F)
```

### Question 1
A recent study assessed the effectiveness of a new drug for children with severe asthma. A total of 10 children with asthma enrolled in the study. The number of asthma attacks that each child has during a 5 day observation period are measured both before and after taking the new medication for two weeks. Below is the data collected in a table called asthma_data. (2 points) <p>

i) Based on the study description, which nonparametric test is most appropriate for analyzing the data shown above? <p>
(a) Kruskal Wallis <p>
(b) Wilcoxon Rank-Sum <p>
(c) Wilcoxon Sign-Rank <p>

```{r}
# SOLUTION: C
```


ii) Write a line of R code to analyze the data using the test you chose for Question 1.1. Use any or all of the following variable names and/or dataset name in your code: "before_group", "after_group", "asthma_data". Hint: The pull( ) function may be helpful.

\
\
Your answer here:
\
\

```{r}
#**Solution**: wilcox.test(asthma_data %>% pull(before_group), asthma_data %>% pull(after_group), paired=T, correct = F)
```


### Question 2
In what circumstances would you choose to conduct a nonparametric test instead of parametric test? Provide exactly 2 reasons. (2 points) <p>
\
\
Your answer here: \
\
\

```{r}
#**Solution**:
# They do not use means or standard deviations
# Use a ranking of the data instead of actual values
# Do not assume a normal distribution of the data
# Less sensitive to outliers and skewed data
# Do not need a large sample size <p>
```

### Question 3
This question draws upon the lecture example about the relationship between the number of registered powerboats and the number of manatee deaths in Florida between 1977 and 2016.

i) Calculate the upper and lower bound for the 95% confidence interval of a coefficient from a regression analysis of the relationship between powerboat purchases and manatee deaths.  Use the following outputs from R in your calculations. Round to 2 decimal places. (1 point) <p>

(a) (0.13, 0.17) <p>
(b) (0.11, 0.14) <p>
(b) (0.12, 0.15) <p>

```{r}
# SOLUTION C
```


ii) Select the correct null and alternative hypothesis for the regression model shown above. (2 points) <p>

(a) Null: There is no association between powerboat purchases and manatee deaths.<p>
(b) Alternative: There is an association between powerboat purchases and manatee deaths. <p>
(c) Alternative: There is no association between powerboat purchases and manatee deaths. <p>
(d) Null: There is an association between powerboat purchases and manatee deaths.<p>


```{r}
# SOLUTION: A, B
```

### Question 4
Historically, 13.7% of adolescents in California The figure below shows four 95% confidence intervals for the proportion of surveyed adolescents that had used e-cigarettes. (3 points) <p>


i) Consider a SRS of 199 adolescents in California, where 37 adolescents had used e-cigarettes. Calculate the standard error of the sampling distribution under the null hypothesis.  (1 point) <p>

\
\
Your answer here: \
\

```{r}
#**Solution**: 0.024 <p>
```


ii) Calculate the z-test for the proportion. Round your answer to two decimal places. (1 point) <p>

\
\
Your answer here: \
\


```{r}
# SOLUTIOn: -1.75 <p>

```

iii) Write a line of R code to calculate the probability of seeing a z-value of this magnitude or larger. (1 point) <p>
\
\
Your answer here: \
\


```{r}
#**Solution**: pnorm(q = -1.75, lower.tail = F)
```

