---
title: "Quiz 3"
author: "Andrew Liu"
output: word_document
---

```{r, include = F}
knitr::opts_chunk$set(include = F, echo = F)
```


### Question 1 [1 point]

**If P(A|B) = P(A) is true then which of the following statements are true? (1 point)**

I. P(B|A) = P(B) is true
II. P(A and B) = P(A) * P(B) is true

\
(a) only I is true \
(b) only II is true \
(c) both II and I are true \
(d) neither I or II is true \

\
\

```{r}
#SOLUTION: both II and I are true
```

\newpage

## Question 2 [1 point]

**Imagine a new screening test is developed to predict whether or not a person has diabetes. Assume you have a population of 200 people of which you know 100 have diabetes and 100 do not. The test correctly detects 80 cases of diabetes and incorrectly detects 5 cases of diabetes. Calculate the PPV of this test, rounded to the nearest whole number with a percent sign (ie 8/10 = 80%):**
\
Your answer here:
\

```{r}
#SOLUTION: 94%
```

\newpage
## Question 3 [1 points]

**iThe 2020 Summer Olympics have been postponed to 2021. In preparation, the International Olympic Committee wants a screening test that will correctly identify a high proportion of athletes who use illegal performance enhancing drugs. On the other hand, the athletes are concerned about a screening test that will incorrectly identify persons as using illegal performance-enhancing drugs when, in fact, they are not using them. Which of the following screening test characteristics are important to each group? (1 point)**

\
(a) High sensitivity for Olympic officials and high specificity for athletes \
(b) High specificity for Olympic officials and high sensitivity for athletes \
(c) High positive predictive value for Olympic officials and high sensitivity for athletes \
(d) High specificity for Olympic officials and high predictive value negative for athletes \

\
\


```{r}
#SOLUTION: High sensitivity for Olympic officials and high specificity for athletes
```
\newpage
## Question 4 [1 point]
**4) True or False. A high sensitivity does not necessarily correspond to a high PPV. (1 point)** 
\
(a) true \
(b) false \

\

```{r}
#SOLUTION: true
```

\newpage

## Question 5 [1 point]

**5) **What function would you use to calculate how much of your assumed normal distribution (in percentages) is below a specific value. For example: given a mean of 5 and an SD of two, what function would you use to calculate how much of your distribution lies from - ∞ to 3.5?**
\

```{r}
#Solution: pnorm()
```

\
\ 
Your answer here:
\

\newpage

## Question 6 [2 points]

**Imagine we sample a random set of undergraduate students and obtain the following data.**

**i) What is the complement of the union of C and B?
Round to the nearest whole number with a percent sign (ie 8/10 = 80%):**
\
your answer here:
\
```{r}
#Solution: 13%
```

**ii) what is the probability of being a coffee drinker and NOT an individual who regularly eats breakfast?  Round to the nearest whole number with a percent sign (ie 8/10 = 80%):**
\
your answer here:
\
```{r}
#Solution: 25%
```


\newpage

## Question 7 [1 point]

**When disease prevalence in a population increases which of the following is true?**
\
(a) Sensitivity increases \
(b) Specificity increases \
(c) Positive predictive value increases \
(d) Negative predictive value increases \

\
\
```{r}
#Solution: Positive predictive value increases
```
