---
title: "PH 142 Quiz 5 Spring 2021"
author: "Your name here"
output: word_document
---

## Instructions
Return via email as a Word document to ph142@berkeley.edu. Do not handwrite your answers or convert to a PDF. Please highlight your answer(s) for any multiple choice questions and type your answer where indicated for short answer or fill in the blank questions.

### Question 1
**The annual global average of deaths from unprovoked shark bites is 4 deaths per year.** <p>
\
**(i) What distribution would be best to model this rare event? (1 point)** <p>

(a) Binomial <p>
(b) Normal <p>
(c) Poisson <p>
\

```{r eval=FALSE, include=FALSE}
#**Solution**: (c) Poisson 
```

**(ii) What are the mean and standard deviation of this distribution? (Assume units of deaths/year for both) (1 point)** <p>

(a) mean = 4; sd = 4 <p>
(b) mean = 16; sd = 16 <p>
(c) mean = 2; sd = 4 <p>
(d) mean = 4; sd = 16 <p>
(e) mean = 4; sd = 2 <p>
(f) mean = 16; sd = 4 <p>
(g) mean = 2; sd = 2 <p>
\
```{r eval=FALSE, include=FALSE}
#**Solution**: (e) mean = 4; sd = 2
```

**(iii) Which of the below equations will correctly calculate the probability of 6 unprovoked shark bite fatalities in a single year? (1 point)** <p>

(a) $P(X = 6) = \frac{e^{-6}6^4}{4!}$ <p>
(b) $P(X \geq 6) = \frac{e^{-4}4^6}{6!}$ <p>
(c) $P(X \geq 6) = \frac{e^{-2}2^6}{6!}$ <p>
(d) $P(X = 6) = \frac{e^{-4}4^6}{6!}$ <p>
(e) $P(X \leq 6) = \frac{e^{-6}6^4}{4!}$ <p>
(f) $P(X = 6) = \frac{e^{-6}6^2}{2!}$ <p>
\
```{r eval=FALSE, include=FALSE}
#**Solution**: (d) $P(X = 6) = \frac{e^{-4}4^6}{6!}$ 
```

**(iv) Which line of `R` code below will correctly calculate the probability of 6 unprovoked shark bite fatalities in a single year? (1 point)** <p>

(a) `ppois(q = 6, lambda = 4, lower.tail = FALSE)` <p>
(b) `dpois(x = 6, lambda = 4)` <p>
(c) `ppois(q = 4, lambda = 6)` <p>
(d) `1 - dpois(x = 6, lambda = 4)` <p>
(e) `1 - ppois(q = 6, lambda = 4)` <p>
(f) `1 - dpois(q = 4, lambda = 6, lower.tail = FALSE)` <p>

```{r eval=FALSE, include=FALSE}
#**Solution**: (b) `dpois(x = 6, lambda = 4)` 
```
\
**(v) Which of the following expressions represents the probability of no more than 1 unprovoked shark bite fatalities in a single year? (1 point)** <p>

(a) $P(X = 1)$ <p>
(b) $1 - [P(X = 0) * P(X = 1)]$ <p>
(c) $P(X = 0) + P(X = 1)$ <p>
(d) $P(X = 0)$ <p>
(e) $1 - [P(X = 0) + P(X = 1)]$ <p>
(f) $P(X = 0) * P(X = 1)$ <p>
(g) $1 - P(X = 0)$ <p>

```{r eval=FALSE, include=FALSE}
#**Solution**: (c) $P(X = 0) + P(X = 1)$
```

### Question 2
**For the next few questions, choose the answer that best replaces the corresponding blank space in the following sentence:** <p>

**The Central Limit Theorem ensures that the _____(i)_____ distribution of the sample mean is _____(ii)_____ as the _____(iii)_____ increases with mean _____(iv)_____ and standard deviation _____(v)_____.** <p>

**(i) (1 point):** <p>

(a) population <p>
(b) sample <p>
(c) sampling <p>
(d) Normal <p>
\
```{r eval=FALSE, include=FALSE}
#**Solution**: (c) sampling
```

**(ii) (1 point):** <p>

(a) Binomial <p>
(b) approximately Binomial <p>
(c) Normal <p>
(d) approximately Normal <p>

```{r eval=FALSE, include=FALSE}
#**Solution**: (d) approximately Normal
```
\
**(iii) (1 point):** <p>

(a) sample size <p>
(b) number of samples <p>
(c) sample mean <p>
(d) population mean <p>

```{r eval=FALSE, include=FALSE}
#**Solution**: (a) sample size
```
\
**(iv) (1 point):** <p>

(a) $\mu$ <p>
(b) $\bar{x}$ <p>
(c) $\bar{X}$ <p>
(d) $x$ <p>
(e) $\sqrt{\mu}$ <p>
(f) $X$ <p>

```{r eval=FALSE, include=FALSE}
#**Solution**: (a) $\mu$
```
\
**(v) (1 point):** <p>

(a) $\sigma$ <p>
(b) $\frac{\sigma}{n}$ <p>
(c) $\frac{\sigma}{\sqrt{n}}$ <p>
(d) $\sigma^2$ <p>
(e) $\frac{\sigma^2}{n}$ <p>
(f) $\frac{\sigma^2}{\sqrt{n}}$ <p>

```{r eval=FALSE, include=FALSE}
#**Solution**: (c) $\frac{\sigma}{\sqrt{n}}$
```
